Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-17 paper.tex
formatting changes for spacing

@@

\subsection{Model Architecture}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library. This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.\\

This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step. After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively. The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is "unpacking" higher-dimensional features from its low-dimensional latent representation. After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier. Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions. This final convolution uses the sigmoid function as its activation function. All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

\subsection{Data Generation}
Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.\\

The NoisyOffice data provided by Kaggle contains 144 ground truth images, 144 training images, and 72 validation images. For the Augraphy model, we produced a dataset 10x larger, by duplicating each of the ground truth images, then running 10 Augraphy pipelines against each copy. Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.\\

@@

In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.\\

@@

\subsection{Training Regime}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

Training proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs. The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.\\

@@

\subsection{Results}
Sample predictions from each model on the validation task are presented in Figure 1. As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue. The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features. Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.\\

@@

\subsection{Additional Techniques}
For brevity, this article only includes experimental results for one type of model. We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion and generative adversarial networks, and ensembles of these. During the validation task, the naive Augraphy model correctly removed the page fold and wrinkle noise, but visually degraded regions of the foreground text. By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output. Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.\\

@@

\subsection{Augraphy Enhancements}
Several upgrades to the Augraphy library itself are also planned.

\subsubsection{Scaling}
While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.

\subsubsection{Performance}
The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware. Performance enhancements to the library are already underway, which will decrease pipeline execution time dramatically, enabling faster creation of larger datasets on more common hardware.

>>>>

% Spacing around floats
\setlength{\floatsep}{11pt plus 2pt minus 4pt}
\setlength{\textfloatsep}{11pt plus 2pt minus 4pt}
\setlength{\dblfloatsep}{\floatsep}
\setlength{\dbltextfloatsep}{11pt plus 2pt minus 4pt}
\setlength{\intextsep}{\floatsep}
\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}

@@

\subsection{Model Architecture}
To evaluate Augraphy, we trained a U-net convolutional neural network, built with the Keras library.
This network achieved a high score on the NoisyOffice Kaggle competition \footnote{\url{https://www.kaggle.com/code/michalbrezk/denoise-images-using-autoencoders-tf-keras/notebook}}; we selected this one for its simplicity and the clarity of its exposition, and use it with few changes.

This low-layer model contains two layers of a convolution, each followed by a rectified linear unit activation function, then a batch normalization layer as the encoding step.
After the encoding step, max pooling is applied, followed by dropout, to improve translation invariance of feature encoding and to avoid overfitting respectively.
The decoding step closely mirrors the encoding step, and contains two layers of ReLU-activated convolutions followed by a batch normalization layer, but with the convolution dimensions reversed; in this case the model is ``unpacking" higher-dimensional features from its low-dimensional latent representation.
After the decoding step, we perform 2-dimensional upsampling, compensating for the 2D max pooling applied earlier.
Finally, the output of previous layers is convolved with a 3x3 kernel, while retaining the same image dimensions.
This final convolution uses the sigmoid function as its activation function.
All convolution steps use a 3x3 kernel and pad edges with zeroes, the max pooling and upsampling steps both use 2x2 kernels, and a 50\% unit dropout rate was used.

\subsection{Data Generation}
Despite recent techniques [Training Vision Transformers with Only 2040 Images, Vision Transformer for Small-Size Datasets, Training a Vision Transformer from scratch in less than 24 hours with 1 GPU] for reducing the volume of input data required to train models, data remains king; feeding a model more data during training can help ensure better latent representations of more features, improving robustness of the model and increasing its ability to generalize.

The NoisyOffice data provided by Kaggle contains 144 ground truth images, 144 training images, and 72 validation images.
For the Augraphy model, we produced a dataset 10x larger, by duplicating each of the ground truth images, then running 10 Augraphy pipelines against each copy.
Doing this was trivial; Augraphy's value lies in its ease of use in producing large training sets.

@@

In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.

@@

\subsection{Training Regime}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.

Training proceeded for 600 epochs or until the model began to overfit, with an overfit patience of 30 epochs.
The NoisyOffice model finished training after 416 epochs, while the Augraphy model trained for the full 600 epochs.

@@

\subsection{Results}
Sample predictions from each model on the validation task are presented in Figure 1.
As expected, the NoisyOffice model performs admirably, but does struggle to fully remove the coffee stain feature, leaving some residue.
The Augraphy model clearly outperforms the NoisyOffice model at stain removal, but does not generalize well to the folding and wrinkling noise; this was expected, since the Augraphy training data did not include fold or wrinkle features.
Further, the Augraphy model overcompensates for the \texttt{BadPhotoCopy} behavior on text, by increasing the line thickness in the predicted text, resulting in a bold font.

@@

\subsection{Additional Techniques}
For brevity, this article only includes experimental results for one type of model.
We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion and generative adversarial networks, and ensembles of these.
During the validation task, the naive Augraphy model correctly removed the page fold and wrinkle noise, but visually degraded regions of the foreground text.
By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output.
Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.

@@

\subsection{Augraphy Enhancements}
Several upgrades to the Augraphy library itself are also planned:

%\subsubsection{Scaling}
\smallskip\noindent\textbf{Scaling.} ~While much work has gone into tuning Augraphy's defaults, and we feel that the effects produced are quite realistic, none of the augmentations were designed to be scale-invariant, and so we plan to introduce pre-trained networks into the library to generate effects in the future.

%\subsubsection{Performance}
\smallskip\noindent\textbf{Performance.} ~The authors typically run substantial Augraphy jobs on enthusiast or datacenter hardware.
Performance enhancements to the library are already underway, which will decrease pipeline execution time dramatically, enabling faster creation of larger datasets on more common hardware.
